analysis

### 2019-12-06 03_Preliminary_analysis.Rmd
Correct code and focus more on both DMI

```{r PA_Libraries, include=FALSE}
library(tidyverse)
library(bomrang)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(lme4)
library(theme.usq)
source("R/import_data.R")
#source("./getPPD2.R")
```

@@

#remove the variation in different sulphur formulations
unique(PM_MB_means[
   grep("sulphur",PM_MB_means$fungicide),
   "fungicide"])
PM_MB_means[grep("sulphur",PM_MB_means$fungicide),"fungicide"] <- "sulphur"

@@

First lets investigate the difference in the effect of fungicide on proportion of yield saved?

```{r Fungicide_x_nSprays_tble, message=FALSE}
PM_MB_means %>%
   group_by(fungicide, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

Plot one and two applications of the main sprays

@@

PM_MB_means[PM_MB_means$fungicide_ai == "sulphur (SC)"|
               PM_MB_means$fungicide_ai == "sulphur (WP)"|
               PM_MB_means$fungicide_ai == "sulphur (Ultra SC)","fungicide_ai"] <- "sulphur"

PM_MB_means$sprays <- sapply(PM_MB_means$total_fungicide, FUN = function(x){if(x == 1){return("one")}else{return("plus")}})

@@

PM_MB_means %>%
   mutate(fungicide_ai = as.factor(PM_MB_means$fungicide_ai)) %>%
#   filter(total_fungicide == 1 | total_fungicide == 2) %>%
   filter(
      fungicide_ai != "pyrazophos" &
         fungicide_ai != "control" &
         fungicide_ai != "benomyl" &
         fungicide_ai != "Acibenzolar-S-methyl") %>%
   mutate(fungicide_ai = factor(fungicide_ai, 
                             levels = c("carbendazim", "pyraclostrobin",
                                        "sulphur", "200 g/L azoxystrobin + 80 g/L cyproconazole",
                                        "tebuconazole", "propiconazole", 
                                        "200 g/L tebuconazole + 120 g/L azoxystrobin"))) %>%
   ggplot(aes(y = prop_YG, x = fungicide_ai)) +
   facet_grid(rows = vars(sprays)) +
   geom_boxplot(aes(fill = fungicide_ai, alpha = 0.5)) +
   geom_hline(aes(yintercept = 0), size = 0.5) +
   labs(y = "Proportion of grain yield saved",
        title = "Grain yield proportion saved\ngrouped by Fungicide type") +
   theme_usq() +
   theme(legend.position = "none") +
   coord_flip()

@@

```{r tebu_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          dose_ai.ha,
          total_fungicide) %>%
   ggplot(aes(x = as.factor(dose_ai.ha))) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
   geom_bar() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

#### Timing of fungicide sprays

### Mungbean cultivars  
Host genotype may need to be analysed to determine the effect.

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole",
         row_spacing == 0.75) %>%
   group_by(host_genotype, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in tebuconazole trials with 0.75 m row spacing") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

@@

>>>>

```{r PA_Libraries, include=FALSE}
library(tidyverse)
library(bomrang)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(devtools)
library(reshape2)
library(lme4)
library(theme.usq)
source("R/import_data.R")
#source("./getPPD2.R")
```

@@

#remove the variation in different sulphur formulations
unique(PM_MB_means[
   grep("sulphur",PM_MB_means$fungicide_ai),
   "fungicide_ai"])
PM_MB_means[grep("sulphur",PM_MB_means$fungicide_ai),"fungicide_ai"] <- "sulphur"

@@

First lets investigate the difference in the effect of the type of fungicide on proportion of yield saved?

```{r Fungicide_x_nSprays_tble, message=FALSE}
PM_MB_means %>%
   group_by(fungicide_ai, total_fungicide) %>%
   summarise(
      n = length(prop_YG),
      lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
      median = median(prop_YG, na.rm = T),
      mean = mean(prop_YG, na.rm = T),
      upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))
   ) %>%
   filter(n >= 5) %>% # remove any fungicide groups with less than 5 observations
   arrange(desc(median)) %>%
   kable(caption = "Fungicide effect on proportion of yield gain.") %>%
   kable_styling(fixed_thead = T, full_width = T) %>%
   footnote(general = "Fungicides with less than five observations were omitted from this table")

@@

Lets visualise this in a plot for one and two sprays only.

@@

@@

@@

```{r tebuAndPropi_dose}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole"|
             fungicide_ai == "propiconazole") %>%
   select(trial_ref,
          year,
          location,
          first_sign_disease,
          fungicide_ai,
          dose_ai.ha,
          total_fungicide) %>%
   ggplot(aes(x = as.factor(dose_ai.ha), fill = fungicide_ai)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Total number of treatments for each respective tebuconazole dose") +
   geom_bar() +
   facet_grid(rows = vars(fungicide_ai))+
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```

There is much variation in the propiconazole dose, lets inspect the difference in yields for each dose.

```{r PropiDoseEffect}
PM_MB_means %>%
   filter(fungicide_ai == "propiconazole") %>%
   ggplot(aes(x = relevel(as.factor(dose_ai.ha),"62.5"), y = prop_YG)) +
   xlab("Dose (g ai/ha)") +
   ggtitle(label = "Yield for each respective propiconazole dose") +
   geom_boxplot() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()

@@

Lets look at the frequency of sprays per fungicide.
```{r Fungicide_x_nSprays}
table(PM_MB_means$fungicide_ai, PM_MB_means$total_fungicide)

PM_MB_means[PM_MB_means$fungicide_ai == "control"
               ,]

#### Timing of fungicide sprays  
When are fungicides sprayed in relation to first sign.

```{r spray_relative2FS}
PM_MB_means %>%
   mutate(s1_DfromFS = fungicide_application_1 - first_sign_disease,
          s2_DfromFS = fungicide_application_2 - first_sign_disease,
          s3_DfromFS = fungicide_application_3 - first_sign_disease,
          s4_DfromFS = fungicide_application_4 - first_sign_disease,
          s5_DfromFS = fungicide_application_5 - first_sign_disease) %>%
   gather(key = spray, value = n_days, s1_DfromFS, s2_DfromFS, s3_DfromFS, s4_DfromFS, s5_DfromFS)%>%
   ggplot(aes(x = spray, y = n_days))+
   geom_violin()

### Mungbean cultivars  
What role does host genotype have in tolerating disease preasure and is it likely to influence the meta-analysis.

@@

Lets plot a stacked barplot of the number of sprays for both demethylation inhibitors, tebuconazole and propiconazole against each cultivar.

```{r Host_genotype}
PM_MB_means %>%
   filter(fungicide_ai == "tebuconazole"|
             fungicide_ai == "propiconazole")%>%
   group_by(host_genotype, fungicide_ai, trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   ggplot(aes(x = host_genotype, y = Treatments, fill = fungicide_ai)) +
   xlab("Cultivar") +
   ylab("N Trials") +
   ggtitle(label = "Cultivars used in tebuconazole trials") +
   geom_col() +
   scale_fill_usq() +
   scale_colour_usq() +
   theme_usq()
```
